---
title:
  primitiveR readme
output: 
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# primitiveR


## Installation


Development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Ilia-Kosenkov/primitiveR")
```
## Example \#1

```{r}
library(purrr)
library(vctrs)
library(primitiveR)
```
`primitiveR` allows for type-preserving and structure-preserving mappings (at least while `purrr` does not fully support it).

```{r}
mtcars[1:5,1:3] %>% map(~.x)
mtcars[1:5,1:3] %>% vmap(~.x)
```

The `*map_pt` version has an optional `.ptype` argument that can be used to select the output type. By default, it will result into the following:
```{r}
mtcars[1:3,1:3] %>% vmap(~.x) -> x
x
x %>% vmap_pt(~.x)
```

```{r}
1:10 %>% vmap_if(~.x > 5, ~1L, .else = ~0L) %>% as_vec
```

## Example \#2
`primitiveR` provides floating-point equality extension using `%==%` and `%!=%`, which operate as normal `==` and `!=` for vector types.

```{r}
0.1 + 0.2 == 0.3
(0.1 + 0.2) %==% 0.3
```
`%===%` and `%!==%` are particular useful in conditions, because these operators apply `all`/`any` to the output of `%==%` or `%!=%`.

```{r}
(1:5) %!=% 1
(1:5) %!==% 1
(1:5) %==% (1:5)
(1:5) %===% (1:5)
```